---
title: "Assignment 1"
author: "Team 6"
date: "2023-02-09"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(dplyr)
library(tidyverse)
library(lattice)
```

```{R}
SP <-read.csv("C:/Users/ritikaa/Desktop/data set for R/StudentsPerformance.csv")
```
#print the structure of the dataset
```{r}
str(SP)
```
#all the variables in the dataset
```{r}
names(SP)
```
#first 15 rows
```{r}
head(SP,15)
```
#userdefined function
```{r}
grpnbr <-function()
{
  print("Hello Team 6")
}
grpnbr()
```
#Reshaping technique
```{r}
SP1 <-SP %>%
  mutate(id = row_number()) %>%
  gather(key = "Subject", value = "Score", math.score, reading.score, writing.score)
head(SP1,10)
```
#filter for math score
```{r}
SP %>% filter(math.score == 89 )
```
#identify duplicate
```{r}
duplicated(SP)
```
#remove duplicate
```{r}
dedupe<-SP[!duplicated(SP),]
dedupe
```
#remove missing values
```{r}
na.omit(SP)
```
#rename the columns
```{r}
names(SP)[names(SP) == "math.score"]<-"subject1"
names(SP)[names(SP) == "reading.score"]<-"subject2"
names(SP)[names(SP) == "writing.score"]<-"subject3"
```
```{r}
head(SP,5)
```
#descending order for subject 1
```{r}
des <- SP %>%
 arrange(desc(subject1))
head(des,15)
```
#random number generator engine
```{r}
sample.int(100, 5)
```
#Print the summary statistics of your datasheet
```{r}
summary(SP)
```
#mode
```{r}
find_mode <- function(x1) 
  {
m <- unique(x1)
tab <- tabulate(match(x1, m))
m[tab == max(tab)]
}
find_mode(SP$subject1)
```
#mean
```{r}
mean(SP$subject2)
```
#median
```{r}
median(SP$subject1)
```
#range
```{r}
range(SP$subject3)
```
#scatter plot for 2 variables
```{r}
plot(SP$subject1,SP$subject3,pch = 19, col="blue")
```
#bar plot for 2 variables
```{r}
sp_new <- SP %>% mutate(id = row_number())
barplot(head(sp_new$subject3,5),head(sp_new$id,5), col = "pink")

```
#corelation between 2 variables
```{r}
cor(SP$subject2,SP$subject3)
```






